Bayesian Networks for Assessing Environmental Sustainability in Australian Vineyards

### 2024-06-11 article.tex
results template to get started on descriptions

\label{figure:generalBN}

@@

TODO: compare these relationships to that of leximancer

\subsection{Sustainability specifics: Coonawarra Winegrowing}
        Sustainability in Coonawarra Winegrowing: Key Factors and Influences
    #TODO: what are the regional specifics of coonawarra
    How do the identified key factors vary across different wine regions in Australia, and what regional characteristics influence these variations?
        Purpose: Examine regional differences and tailor sustainability strategies.
        Results: Compare the generic model to the Coonawarra model. Acknowledge there is more work to be done here due to the amount of regions across Australia and the world. Prevous work also helps to illustrate these differences.

    How do changes in key factors under various environmental and regulatory scenarios influence the overall environmental impact in Coonawarra?
        Purpose: Assess different factors overall influence to environmental sustainability given the definitions used.
        Results: Use the CPT values to assess the significant contribution of different variables on the BN and how that effects environmental sustainability.

Figure Marcel + robyn BNs

>>>>

\begin{figure}[h!]
    \centering
    % \includegraphics[width=\textwidth]{path_to_coonawarra_bn_figure} % Adjust the width as needed
    \caption{The resultant Bayesian network after initial discussions of how factors that contribute to environmental impact are related. Illustrating the general relationships that exist between vineyard factors and environmental impact in Australian winegrowing.}
    \label{fig:generalBN}
\end{figure}

@@

% TODO: compare these relationships to that of leximancer

\subsection{Sustainability specifics: Coonawarra Winegrowing}
    %     Sustainability in Coonawarra Winegrowing: Key Factors and Influences
    % #TODO: what are the regional specifics of coonawarra
    % How do the identified key factors vary across different wine regions in Australia, and what regional characteristics influence these variations?
    %     Purpose: Examine regional differences and tailor sustainability strategies.
    %     Results: Compare the generic model to the Coonawarra model. Acknowledge there is more work to be done here due to the amount of regions across Australia and the world. Prevous work also helps to illustrate these differences.

    % How do changes in key factors under various environmental and regulatory scenarios influence the overall environmental impact in Coonawarra?
    %     Purpose: Assess different factors overall influence to environmental sustainability given the definitions used.
    %     Results: Use the CPT values to assess the significant contribution of different variables on the BN and how that effects environmental sustainability.

\begin{figure}[h!]
    \centering
    % \includegraphics[width=\textwidth]{path_to_coonawarra_bn_figure} % Adjust the width as needed
    \caption{Coonawarra-specific Bayesian Network illustrating key factors impacting environmental sustainability, with nodes coloured by sensitivity to environmental impact.}
    \label{fig:coonawarra_bn}
  \end{figure}

% TODO: the exclusion of renewable fuels due to none being used in coonawarra
% the difference in vineyard floor management and its relationship to tractors
% The influence of compost, soil depth and clay content. although not specifically significant due to not listing the CPTs - it was highlighted as significant with different influence values depending on the direct field in question and not just which vineyard.
% variation occurs all the way to the vine level!

  This subsection examines how the identified key factors impacting environmental sustainability vary across different wine regions in Australia, with a focus on Coonawarra. By comparing the generic Bayesian Network (BN) model to the Coonawarra-specific model (Figure \ref{fig
  } and Figure \ref{fig
  }), we identify regional characteristics that influence these variations.

  The comparison reveals that while some factors, such as water use and agrochemical legislation, remain consistently significant, other factors like soil management practices show regional variation. The Coonawarra model highlights the unique environmental and regulatory conditions specific to this region, indicating a need for tailored sustainability strategies. It is important to acknowledge that this analysis is preliminary and further work is required to cover the numerous wine regions across Australia and globally. Previous studies have also illustrated similar regional differences, underscoring the complexity and necessity of localised sustainability assessments.

  By using Conditional Probability Tables (CPTs) within the BN, the significant contributions of different variables to environmental sustainability in Coonawarra were assessed. Figures \ref{fig
  } and \ref{fig
  } illustrate these networks with nodes coloured according to their sensitivity values relative to environmental impact.

  The CPT values allow for an in-depth analysis of how changes in key factors, under various environmental and regulatory scenarios, influence the overall environmental impact. For instance, the Coonawarra-specific model demonstrates that changes in water management practices have a higher sensitivity to environmental impact compared to the generic model. This highlights the critical areas where regulatory and environmental interventions could have the most substantial effect.

  By assessing the BN, it becomes evident which factors are the most influential in driving environmental sustainability in Coonawarra. This detailed evaluation helps prioritize actions and policies that could lead to significant improvements in the region's sustainability practices.
